Functional Analysis of CGM Data

### 2022-12-02 StatNet/cgm_fda.qmd
Update cgm_fda.qmd

# Limit to first day with no missing

@@

@@

@@

```{r}
#| include: false
# load("~/Dropbox/Work/Vigers/CF/Christine Chan/CGM and FDA/R_Objects/fpca_sc_fit.Rdata")
```

@@

-   I'm having some trouble running

>>>>

# Limit to first day with enough data (50 obs. for now, but that's ad-hoc)
keep = sapply(glucs, function(g){sum(!is.na(g))>=50})

@@

-   The FPCA model is of the form:

$$Y_i(t)=\mu(t)+\sum_{k=1}^{K}c_{ik}\psi_k(t)+\epsilon_{i}(t) $$

-   $\mu(t)$ is the population mean
-   $\psi_k(t)$ are a set of population-level basis functions
-   $c_{ik}$ are subject-specific scores with mean zero and variance $\lambda_k$
-   $\epsilon_i(t)$ are residual curves
-   There is an eigenfunction associated with each eigenvalue, rather than an eigenvector.
-   These eigenfunctions describe major variational components, but in function form

## Function-on-Scalar Regression

-   The most common FoSR model is:

$$Y_i(t)= \beta_0(t) + \sum_{k=1}^{p}x_{ik}\beta_k(t) + \epsilon_i(t)$$

-   $\beta_k(t)$ are fixed effects associated with scalar covariates and the $\epsilon_i(t)$ are residual curves.
-   $\beta_k(t)$ are interpreted analogously to coefficients in a multiple linear regression

@@

## FPCA on This Dataset

```{r}
#| include: false
load("~/Dropbox/Work/Vigers/CF/Christine Chan/CGM and FDA/R_Objects/fpca_sc_fit.Rdata")
```

```{r}
knitr::kable(head(ydf))
```

@@

## Function-on-Scalar Regression for Our Data

```{r}
#| include: false
ydf_wide = 
  ydf %>% group_by(.id) %>% 
  filter(row_number() <= 54) %>%
  mutate(.index = row_number()) %>%
  pivot_wider(id_cols = .id,names_from = .index,values_from = .value,names_prefix = "glucose_")
ids = ydf_wide$.id
ydf_wide$.id = NULL
ydf_wide = data.matrix(ydf_wide)
rownames(ydf_wide) = ids
sleep$Glucose = ydf_wide
sleep$Group = factor(sleep$Group,ordered = F)
sleep = na.omit(sleep)
```

```{r}
#| echo: true
fosr_mod = bayes_fosr(Glucose ~ Group,data = sleep) 
```

```{r}
data(DTI)
DTI = subset(DTI, select = c(cca, case, pasat))
DTI = DTI[complete.cases(DTI),]
DTI$gender = factor(sample(c("male","female"), dim(DTI)[1], replace = TRUE))
DTI$status = factor(sample(c("RRMS", "SPMS", "PPMS"), dim(DTI)[1], replace = TRUE))
## fit models
dti_fosr_mod = bayes_fosr(cca ~ gender, data = DTI)
```

@@

-   Does this even seem like the correct approach?
-   Really what we want to do is classify people based on CGM tracing. Is there a good package for functional discriminant analysis?
-   FoSR in `refund` requires complete data, so how do we deal with irregular sampling across CGM tracings
    -   There is between and within-subject variability in terms length of sleep and therefore number of glucose measures
-   What does it mean that the FPCA eigenfunctions are essentially flat?
-   I'm having some trouble running the full dataset, even on a relatively beefed up desktop. Any recommendations?
-   Recommendations for easier to use packages?
    -   Data formatting is a nightmare with the various FDA packages, and unfortunately `tidyfun` is pretty limited.
